---
title: "Bahia Lomas Red Knot report, tables and figures"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message=FALSE, fig.width = 6.5)
if (!requireNamespace("pacman", quietly = TRUE)) install.packages("pacman", quiet = TRUE)
if (!requireNamespace("remotes", quietly = TRUE)) install.packages("remotes", quiet = TRUE)
if (!requireNamespace("nrsmisc", quietly = TRUE)) remotes::install_github("adamdsmith/nrsmisc")
if (!requireNamespace("ggmap", quietly = TRUE)) remotes::install_github("dkahle/ggmap")
pacman::p_load(reshape, raster, dplyr, tidyr, lubridate, sf, rnaturalearth, motus, nrsmisc, 
               oce, RStoolbox, ggplot2, ggmap, scales)
source("R/detection_loc.R")
source("R/show_active_recv.R")
source("R/geo_helpers.R")
source("R/tides.R")
get_update <- FALSE
# Set Google Maps API key
register_google(Sys.getenv("goog_key"))
```

```{r tag_detections, cache=TRUE}
# Bahia project
proj <- 174

# Tag deployments
rekn_deploy <- read.csv("Data/tag-deployments.csv", stringsAsFactors = FALSE) %>%
  filter(deploymentStatus == "active",
         !is.na(latitude)) %>%
  mutate(spp = toupper(gsub("(\\b[A-Z][a-z])|.", "\\1", motusEnglishName))) %>%
  select(tagID, tagPL = period, species = motusEnglishName, spp, age, weight)

# Full detection history
# Last updated 27 March 2019
rekn_full <- tagme(proj, update = get_update, forceMeta = TRUE, dir = "Data/") %>%
  tbl("alltags") %>% collect() %>% as.data.frame()

# Detection histories
rekn <- rekn_full %>% 
  # Join with deployment info
  left_join(rekn_deploy, by = c("motusTagID" = "tagID")) %>%
  filter(motusTagID %in% rekn_deploy$tagID,   # Only Bahia Lomas project (#174) tags
         runLen > 2,                          # Basic filter
         freqsd < 0.075,                      # Basic filter
         !is.na(tagDeployLat),                # Omits one apparent test deployment?
         ts > tagDeployStart,                 # Detections occur after deployment
         grepl("BahiaLomas", fullID)) %>%     # Only Bahia Lomas project (#174) tags
  mutate(ts = as_datetime(ts, tz = "UTC"),
         tagDeployEnd = as_datetime(tagDeployEnd, tz = "UTC"),
         tagDeployStart = as_datetime(tagDeployStart, tz = "UTC"),
         date = as.Date(ts),
         ts_hour = as.POSIXct(round(ts, "hours")),
         chile = recvProjID == 174,
         label = paste(spp, motusTagID, sep = "_")) %>%
  group_by(motusTagID) %>%
  mutate(since_rel = as.numeric(difftime(ts, tagDeployStart, units = "days"))) %>%
  select(spp, age, weight, motusTagID, mfgID, tagBI, tagDeployStart, tagDeployEnd, 
         date, ts, ts_hour, chile, since_rel, sig, runID, runLen, freqsd,
         recvSiteName, recvDeployID, port) %>%
  arrange(motusTagID, runID, ts)

# Detection length
rekn_times <- rekn %>%
  group_by(spp, age, weight, motusTagID, mfgID, tagDeployStart, tagDeployEnd, chile, recvSiteName, recvDeployID,
           port, runID) %>%
  summarize(det_len = round(as.numeric(difftime(max(ts), min(ts), units = "mins")), 3),
            date = min(date))
# Detection lengths by hour
rekn_times_h <- rekn %>%
  group_by(spp, age, weight, motusTagID, mfgID, tagDeployStart, tagDeployEnd, chile, recvSiteName, recvDeployID,
           port, runID, ts_hour) %>%
  summarize(det_len = round(as.numeric(difftime(max(ts), min(ts), units = "mins")), 3),
            det_len = ifelse(det_len < 0.05, round(min(tagBI)/60, 3), det_len),
            date = min(date),
            sigSD = sd(sig))
rekn_chile <- filter(rekn, chile)
rekn_times_chile <- filter(rekn_times, chile)
rekn_times_h_chile <- filter(rekn_times_h, chile)

chile_summary <- rekn_chile %>%
  group_by(tagDeployStart, spp, add = TRUE) %>%
  # Get first and last Chile detections
  summarize(firstChile = min(ts),
            finalChile = max(ts),
            leave_date = as.Date(finalChile),
            leave_stn = recvSiteName[which.max(ts)]) %>%
  mutate(chileStay = as.numeric(difftime(finalChile, tagDeployStart, units = "days")))
```

```{r receivers, cache=TRUE}
# Network-wide receiver information
motus_recvs_full <- tagme(proj, update = get_update, forceMeta = TRUE, dir = "Data/") %>%
  tbl("recvDeps") %>% collect() %>% as.data.frame()

# Receivers active from tag deployment through July of deploy year
active_recvs <- motus_recvs_full %>%
  filter(!is.na(tsStart), !is.na(latitude)) %>%
  mutate(tsStart = as_datetime(tsStart, tz = "UTC"),
         # for deployments with no end dates, make end date today
         tsEnd = as_datetime(ifelse(is.na(tsEnd), with_tz(Sys.time(), tzone = "UTC"), tsEnd), tz = "UTC"),
         # add variable 'active' that indicates if receiver was active during REKN tag activity
         active = int_overlaps(interval(tsStart, tsEnd),  # receiver interval
                               interval(min(rekn$tagDeployStart), as.POSIXct("2018-07-31")))) %>% # REKN interval
  rename(recvLat = latitude, recvLon = longitude, recvDeployName = name,
         recvStart = tsStart, recvEnd = tsEnd, recvProjID = projectID, recvDeployID = deployID)

compass <- data.frame(antBin = c("N","NNE","NE","ENE","E","ESE", "SE", "SSE","S","SSW","SW","WSW","W","WNW","NW","NNW"),
                      antBinDeg = seq(0, 337.5, by = 22.5),
                      stringsAsFactors = FALSE)

# Bahia Lomas receivers
bahia_recvs <- read.csv("Data/receiver-deployments.csv", stringsAsFactors = FALSE) %>%
  filter(latitude < -50,
         # Buque Quemado never functioned correctly
         !grepl("Buque", siteName))
bahia_ants <- read.csv("Data/antenna-deployments.csv", stringsAsFactors = FALSE) %>%
  select(recvDeployID:antennaType, trueBearing) %>%
  mutate(antBin = get_16wind(trueBearing))
bahia_recvs <- left_join(bahia_recvs, bahia_ants, by = "recvDeployID") %>%
  mutate(tsStart = as_datetime(tsStart, tz = "UTC"),
         tsEnd = as_datetime(tsEnd, tz = "UTC")) %>%
  filter(tsStart < as.POSIXct("2018-07-31")) %>%
  select(recvDeployID, recvSiteName = siteName, tsStart, tsEnd, 
         recvLat = latitude, recvLon = longitude, port, antennaType, antBin) %>%
  left_join(compass, by = "antBin") %>%
  # Approximate center of detection zones for each antenna and add to receiver data
  group_by_all() %>%
  do(detection_loc(.$recvLat, .$recvLon, .$antBinDeg, distkm = 3))

# Duplicate port 1 @ E. Pepita on Port 0; I believe they are synonymous
ep0 <- ungroup(bahia_recvs) %>% filter(recvSiteName == "E. Pepita", port == 1) %>%
  mutate(port = 0)
bahia_recvs <- bind_rows(bahia_recvs, ep0)
```

# Bahia Lomas receiver station activity and detection summary

The receiving station at Buque Quemado never functioned correctly (and thus never detected a single individual) and is excluded from further consideration. All remaining stations comprised three active antennas. Thus, in site-level summaries, we do not attempt to adjust detection numbers or times based on the number of active antennas.

```{r, cache=TRUE, fig.height=2}
dly_recv_log <- ungroup(bahia_recvs) %>% select(recvSiteName:tsEnd) %>%
  distinct() %>% # Drop antenna-related duplicates
  rowwise() %>%
  do(data.frame(recvSiteName = .$recvSiteName, 
                date = seq(as.Date(.$tsStart), as.Date(.$tsEnd), by = "day"))) %>%
  distinct() %>%
  # Dates outside detections irrelevant
  filter(between(date, min(rekn_chile$date), max(rekn_chile$date))) %>%
  # Add down times
  mutate(active = case_when(
    recvSiteName == "E. MiraMar" & between(date, as.Date("2018-02-16"), as.Date("2018-04-05"))     ~ FALSE,
    recvSiteName == "Punta Catalina" & date < as.Date("2018-02-25")                                ~ FALSE, 
    recvSiteName == "Punta Catalina" & between(date, as.Date("2018-03-23"), as.Date("2018-04-04")) ~ FALSE,
    recvSiteName == "Punta Catalina" & between(date, as.Date("2018-04-13"), as.Date("2018-04-26")) ~ FALSE,
    recvSiteName == "Punta Catalina" & between(date, as.Date("2018-05-01"), as.Date("2018-05-11")) ~ FALSE,
    recvSiteName == "Punta Catalina" & between(date, as.Date("2018-05-14"), as.Date("2018-05-19")) ~ FALSE,
    recvSiteName == "Punta Catalina" & date > as.Date("2018-05-22")                                ~ FALSE, 
    TRUE ~ TRUE)) %>%
  # Complete data set over period of interest
  complete(recvSiteName, date, fill = list(active = FALSE))
ggplot(dly_recv_log, aes(date, recvSiteName)) + 
  geom_point(aes(color = active), size =  2) +
  labs(y = "", x = "Date", color = "Active") +
  theme_bw()
dly_recv_count <- filter(dly_recv_log, active) %>% group_by(date) %>% count(name = "n_active_recv")
```

## Number of individuals detected daily across all stations

Total number of individual Hudsonian Godwits (HUGO) and Red Knots (REKN) detected daily by Bahia Lomas receiving stations. Receiver station activity is indicated along the top of the figure.

```{r}
rekn_chile %>% select(date, motusTagID, spp) %>% distinct() %>% 
  group_by(date, spp) %>% count() %>%
  ungroup() %>%
  complete(date, spp) %>%
  ggplot(aes(date, n)) + 
  geom_path() + theme_bw() +
  labs(x = "Date", y = "# individuals detected",
       color = "") +
  scale_y_continuous(breaks = pretty_breaks()) +
  facet_grid(spp ~ ., scales = "free_y") +
  # Add receiver activity
  geom_path(data = show_active_recv(8.5, 0.25, NA_inactive = TRUE, input = dly_recv_log),
            aes(y = y, color = recvSiteName), lwd = 1)
```

# Site-level summary plots

## Weekly total time of detection

Here, for each week, we sum the total time of detection of all individual Hudsonian Godwits (HUGO) and Red Knots (REKN) by receiving station. The corresponding period of activity for each receiving station is indicated along the top of the figure. E. Pepita is the primary site of detection, perhaps not surprisingly given its close proximity to the trapping location. E. MiraMar also detected birds regularly while it was functional. E. El Pantano and Punta Catalina were used much more sparingly, as better illustrated in the next figure.

```{r}
week_midpts <- seq.Date(from = as.Date("2018-01-04"), length.out = 23, by = "week")
week_midpts <- data.frame(midpt = week_midpts,
                          week = lubridate::week(week_midpts))

rekn_times_chile %>% ungroup() %>%
  select(date, motusTagID, recvSiteName, spp, det_len) %>% 
  mutate(week = lubridate::week(date)) %>%
  group_by(week, recvSiteName, spp) %>% 
  summarize(tot_det_len = sum(det_len)/60) %>%
  left_join(week_midpts, by = "week") %>%
  ggplot(aes(midpt, tot_det_len, fill = recvSiteName)) + geom_bar(stat = "identity") + theme_bw() +
  labs(x = "Date", y = "Cumulative detection time (hours)", fill = "", color = "") +
  facet_grid(spp ~ ., scales = "free_y") +
  # Add receiver activity
  geom_path(data = show_active_recv(375, 12.5, NA_inactive = TRUE, input = dly_recv_log), 
            aes(date, y, color = recvSiteName), lwd = 1)
  
```

## Daily total time of detection

Here, for each day, we sum the total time of detection of all individual Hudsonian Godwits (HUGO) and Red Knots (REKN) by receiving station. The corresponding period of activity for each receiving station is indicated in grey. Again, it is clear that E. Pepita is the primary site of detection, with E. MiraMar also detecting birds regularly while it was functional. E. El Pantano was visited consistently but for shorter durations and by fewer individuals (see also next figure). Punta Catalina was used much more briefly and sporadically, and by many fewer individuals, as better illustrated in the next figure.

```{r, fig.height=4}
rekn_times_chile %>% ungroup() %>%
  select(date, motusTagID, recvSiteName, spp, det_len) %>% 
  group_by(date, recvSiteName, spp) %>% 
  summarize(tot_det_len = sum(det_len)/60) %>%
  ggplot(aes(date, recvSiteName)) + 
  # Add receiver activity to background
  geom_point(data = show_active_recv(spp = c("HUGO", "REKN"), input = dly_recv_log), 
             color = "gray70", size = 1) +
  # Detection length
  geom_point(aes(color = tot_det_len, size = tot_det_len)) + 
  scale_size(range = c(1, 10), guide = "none") + theme_bw() +
  scale_color_viridis_c("Cumulative detection time:", trans = "log2", 
                        breaks = c(0.01666, 0.16667, 1, 6, 24, 168, 504), 
                        labels = c("1min", "10min", "1h", "6h", "1d", "1wk", "3wk"),
                        limits = c(NA, 504),
                        guide = guide_colorbar(barwidth = grid::unit(0.5, "npc"), title.vjust = 0.8,
                                               title.position = "left")) +
  facet_grid(spp ~ .) + labs(y = "") +
  theme(legend.position = "top")
```

## Daily number of individuals detected

Here, for each day, we indicate the total number of individual Hudsonian Godwits (HUGO) and Red Knots (REKN) detected by receiving station. The corresponding period of activity for each receiving station is indicated in grey. Again, it is clear that E. Pepita is the primary site of detection, with E. MiraMar also regularly detecting most birds present while it was functional. E. El Pantano was visited consistently by Red Knots, although by fewer individuals that E. Pepita and E. MiraMar. Punta Catalina was visited by only a few individuals on a few occasions in late February and early March.

```{r, fig.height=4}
rekn_chile %>% ungroup() %>%
  select(date, recvSiteName, spp, motusTagID) %>% 
  distinct() %>%
  group_by(date, recvSiteName, spp) %>%
  tally() %>%
  ggplot(aes(date, recvSiteName)) + 
  # Add receiver activity
  geom_point(data = show_active_recv(spp = c("HUGO", "REKN"), input = dly_recv_log), 
             color = "gray70", size = 1) +
  geom_point(aes(color = n, size = n)) + 
  scale_size(range = c(1, 10), guide = "none") + theme_bw() +
  scale_color_viridis_c("# Individuals detected:",
                        guide = guide_colorbar(barwidth = grid::unit(0.25, "npc"),
                                               title.vjust = 0.8,
                                               title.position = "left")) +
  facet_grid(spp ~ .) + labs(y = "") +
  theme(legend.position = "top")
```

Same information as above, illustrated with line graphs rather than point size/color.

```{r, fig.height=4}
rekn_chile %>% ungroup() %>%
  select(date, recvSiteName, spp, motusTagID) %>% 
  distinct() %>%
  group_by(date, recvSiteName, spp) %>%
  tally() %>%
  ungroup() %>%
  complete(recvSiteName, date, spp) %>%
  arrange(spp, recvSiteName, date) %>%
  ggplot(aes(date, n)) + 
  geom_point(aes(group = recvSiteName, color = recvSiteName), size= 1) + 
  geom_path(aes(group = recvSiteName, color = recvSiteName), lwd = 1) + 
  # Add receiver activity
  geom_path(data = show_active_recv(8.5, 0.35, NA_inactive = TRUE, input = dly_recv_log),
            aes(y = y, color = recvSiteName), lwd = 1) +
  scale_y_continuous("# individuals detected", breaks = pretty_breaks(), limits = c(0, NA)) +
  facet_grid(spp ~ ., scales = "free_y") + theme_bw() + labs(color = "")
```

## Last detection by Bahia Lomas station (weekly)

Weekly number of Hudsonian Godwits (HUGO) and Red Knots (REKN) last detected by Bahia Lomas receiving stations. Lines across the top of the HUGO plot illustrate the period that each station was actively listening for tagged birds. Which receivers last detected Red Knots? The site nearest the capture location, E. Pepita, most commonly was the last station of detection for Red Knots, followed by E. El Pantano and E. MiraMar, though their relative importance is somewhat complicated by the fact that E. Miramar was inactive from mid-February through early April and Punta Catalina functioned consistently only through mid/late-March and sporadically thereafter. With that said, the area around Punta Catalina seemed to be used very infrequently by tagged birds relative to E. Pepita in particular, but also E. El Pantano and E. MiraMar when all stations were active (refer to above figures).

```{r}
chile_summary %>%
  ggplot(aes(x = leave_date, color = leave_stn, fill = leave_stn)) +
  geom_histogram(binwidth = 7) +
  geom_path(data = show_active_recv(2.77, 0.1, "leave_stn", NA_inactive = TRUE, input = dly_recv_log), 
            aes(date, y), lwd = 1) +
  scale_y_continuous(breaks = pretty_breaks(n = 4)) +
  facet_grid(spp ~ ., scales = "free_y") + theme_bw() +
  labs(x = "Last week detected", y = "# individuals", color = "", fill = "")
```

## Relative Red Knot detections within and among stations

This distinguishes Red Knot detections by receiving station antenna, showing the apparent relative site use within a station's detection zones as well as among stations. Points are located along the approximate antenna detection axis at a distance of 3 km from the receiving station. This again illustrates that most detections occurred near and northwest of the capture location (red crosshair) at E. Pepita, with considerably shorter total detection duration, and numbers of individuals detected, as one moves east along the southern shore of Bahia Lomas towards Punta Catalina. Note however that the relative use of E. MiraMar is likely considerably underestimated due to station failure from mid-February to early April. See the next figure for a more equitable comparison of the relative use of the three primary detection sites (E. Pepita, E. MiraMar, and E. El Platano). It is important to note that cumulative detection time is also a function of detectability, which is likely to be higher when birds are near the receiving station or flying. Thus, cumulative detection time is likely not strictly an index of site use or importance. 

```{r, fig.height=6, cache=TRUE}
# recvs <- pull(bahia_recvs, recvSiteName) %>% unique()
# recvs <- recvs[c(2,1,3,4)]
ant_avail <- ungroup(bahia_recvs) %>% select(recvSiteName, antBin, det_lon, det_lat) %>% distinct()
rekn_time_ant <- rekn_times_chile %>% ungroup() %>%
  filter(spp == "REKN") %>%
  left_join(bahia_recvs, by = c("recvSiteName", "recvDeployID", "port")) %>%
  select(motusTagID, recvSiteName, antBin, det_lat, det_lon, det_len) %>% 
  group_by(recvSiteName, antBin, det_lat, det_lon) %>%
  summarize(tot_det_len = sum(det_len)/60,
            n_ind = n_distinct(motusTagID)) %>%
  ungroup() %>%
  complete(ant_avail, fill = list(tot_det_len = 0.005, n_ind = 0))

# Create Google Map satellite background (this proved faster to generate figures)
bl <- get_map(location = c(lon = -69.09, lat = -52.57), scale = 4, zoom = 10, maptype = "hybrid")
bl_rast <- ggmap_rast(bl)
projection(bl_rast) <- CRS("+init=epsg:4326") # bounding box projection

# Bring in habitat raster, "fix" extent, filter to intertidal, ection prior to reprojection as sf object
hab <- raster("Data/bahia_lomas_habitats_v3.img") %>%
  shift(x = 200, y = 9999900) %>%
  projectRaster(crs = CRS("+init=epsg:4326"), method = "ngb") %>%
  as.data.frame(xy = TRUE) %>%
  filter(!is.na(bahia_lomas_habitats_v3),
         bahia_lomas_habitats_v3 %in% 2:3) %>%
  select(x, y, hab_code = bahia_lomas_habitats_v3) %>%
  mutate(habitat = ifelse(hab_code == 2, "Mud-dominated", "Sand-dominated"))

site_locs <- group_by(bahia_recvs, recvSiteName) %>% slice(1)

ggRGB(bl_rast) +
  coord_sf(crs = 4326) +
  geom_tile(data = hab, aes(x, y, fill = habitat), alpha = 0.5) + 
  geom_point(data = rekn_time_ant, aes(x = det_lon, y = det_lat,
             size = tot_det_len, color = tot_det_len),
             shape = 21, fill = NA, stroke = 3) +
  scale_size(guide = "none", range = c(5,12)) + theme_bw() +
  scale_fill_manual("Intertidal flat type",
                    values = c("saddlebrown", "khaki1"),
                    guide = guide_legend(order = 1, direction = "vertical")) +
  scale_color_viridis_c("Cumulative detection time:", trans = "log2",
                       breaks = c(0.0166666, 1, 24, 168, 720, 3600),
                       labels = c("1min", "1h", "1d", "1wk", "1mo", "5mo"),
                       limits = c(0.005, 3600),
                       guide = guide_colorbar(order = 2, barwidth = grid::unit(0.4, "npc"), 
                                              title.vjust = 0.8,
                                              title.position = "left")) +
  # Receiving stations locations
  geom_point(data = site_locs, aes(x = recvLon, y = recvLat),
             pch = 7, color = "white", size = 2.5) +
  # Number of individuals detected
  geom_text(data = rekn_time_ant, aes(x = det_lon, y = det_lat, label = n_ind), 
            color = "white", fontface = "bold", size = 3) + 
  annotate("point", x = -69.376211, y = -52.479484, color = "red", pch = 10, size = 3) +
  xlim(c(-69.45, -68.7)) + ylim(c(-52.7, -52.4)) +
  theme(legend.position = "top", 
        axis.text=element_blank(),
        axis.ticks=element_blank(),
        axis.title=element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "cm"))

# rekn_su <- lapply(recvs, function(r) {
#   r_loc_df <- filter(bahia_recvs, recvSiteName == r)[1, c("recvLat", "recvLon")]
#   r_loc <- unlist(r_loc_df) %>% unname()
#   r_bl <- get_map(location = c(lon = r_loc[2], lat = r_loc[1]), zoom = 13, maptype = "satellite")
#   r_tmp <- filter(rekn_time_ant, recvSiteName ==r)
#   ggmap(r_bl, extent = "device",
#         base_layer = ggplot(aes(x = det_lon, y = det_lat), data = r_tmp)) +
#     geom_point(aes(size = tot_det_len, fill = tot_det_len), pch = 21) +
#     scale_size_area(guide = "none") + theme_bw() +
#     scale_fill_viridis_c("detection time (hours):",
#                           guide = guide_colorbar(barwidth = grid::unit(0.15, "npc"), title.vjust = 0.8,
#                                                  title.position = "left")) +
#     geom_point(data = r_loc_df, aes(x = recvLon, y = recvLat),
#                pch = 7, color = "white", fill = "grey50", size = 2) +
#     theme(legend.position = "top",
#           axis.ticks=element_blank(),
#           axis.title=element_blank(),
#           plot.margin = unit(c(0, 0, 1, 0), "cm")) +
#     ggtitle(r)
# })
# cowplot::plot_grid(plotlist = rekn_su, align = "hv", axis = "tblr")

  # Add receiver activity
```

## Relative Red Knot detections within and among stations (peak activity)

Here we focus on the relative use of the three primary detection sites (E. Pepita, E. MiraMar, and E. El Platano) during a period (capture to mid-February) when most individual Red Knots (REKN) were present on the landscape and all three stations were fully functional. Points are located along the approximate antenna detection axis at a distance of 3 km from the receiving station. This again illustrates that the vast majority of detection time occurred near and northwest of the capture location (red crosshair) at E. Pepita, with considerably shorter total detection duration, and numbers of individuals detected, as one moves east along the southern shore of Bahia Lomas towards Punta Catalina. It is important to note that cumulative detection time is also a function of detectability, which is likely to be higher when birds are near the receiving station or flying. Thus, cumulative detection time is likely not strictly an index of site use or importance. 

```{r, fig.height=6, cache=TRUE}
feb_ant_avail <- filter(ant_avail, !grepl("Catalina", recvSiteName))
feb_rekn_time_ant <- rekn_times_chile %>% ungroup() %>%
  filter(spp == "REKN", date <= ymd("2018-02-15")) %>%
  left_join(bahia_recvs, by = c("recvSiteName", "recvDeployID", "port")) %>%
  select(motusTagID, recvSiteName, antBin, det_lat, det_lon, det_len) %>% 
  group_by(recvSiteName, antBin, det_lat, det_lon) %>%
  summarize(tot_det_len = sum(det_len)/60,
            n_ind = n_distinct(motusTagID)) %>%
  ungroup() %>%
  complete(feb_ant_avail, fill = list(tot_det_len = 0.0001, n_ind = 0))
feb_site_locs <- filter(bahia_recvs, !grepl("Catalina", recvSiteName)) %>%
  group_by(recvSiteName) %>% slice(1)

ggRGB(bl_rast) +
  coord_sf(crs = 4326) +
  geom_tile(data = hab, aes(x, y, fill = habitat), alpha = 0.5) + 
  geom_point(data = feb_rekn_time_ant, aes(x = det_lon, y = det_lat,
                                           size = tot_det_len, color = tot_det_len), 
             shape = 21, fill = NA, stroke = 3) +
  scale_size(guide = "none", range = c(5,12)) + theme_bw() +
  scale_fill_manual("Intertidal flat type",
                    values = c("saddlebrown", "khaki1"),
                    guide = guide_legend(order = 1, direction = "vertical")) +
  scale_color_viridis_c("Cumulative detection time:", trans = "log2",
                       breaks = c(1, 24, 168, 720, 2160),
                       labels = c("1h", "1d", "1wk", "1mo", "3mo"),
                       limits = c(1, NA),
                       guide = guide_colorbar(order = 2, barwidth = grid::unit(0.4, "npc"), title.vjust = 0.8,
                                              title.position = "left")) +
  # Receiving stations locations
  geom_point(data = feb_site_locs, aes(x = recvLon, y = recvLat),
             pch = 7, color = "white", size = 2.5) +
  # Number of individuals detected
  geom_text(data = feb_rekn_time_ant, aes(x = det_lon, y = det_lat, label = n_ind), 
            color = "white", fontface = "bold", size = 3) + 
  annotate("point", x = -69.376211, y = -52.479484, color = "red", pch = 10, size = 3) +
  xlim(c(-69.45, -68.7)) + ylim(c(-52.7, -52.4)) +
  theme(legend.position = "top", 
        axis.text=element_blank(),
        axis.ticks=element_blank(),
        axis.title=element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "cm"))
```

## Receiving station detections and association with tides

Here we compare the proportional distribution of tide heights while each receiving station was active (grey background bars) with tide heights during Red Knot (REKN) detections. Detections at E. Pepita and E. El Pantano occur generally across the distribution of tide heights at those sites, with a slightly disproportionate increase in detection rate at some higher water levels (although not extreme high water at E. Pepita). In contrast, REKN are strongly disproportionately detected at E. MiraMar and Punta Catalina during very high tides, suggesting that knots are using these sites preferentially, or that they are restricted to more detectable areas, during very high water. These patterns are fairly consistent across different detection zones around each site; that is, the patterns apply generally around a station.

```{r}
# Load tide model
load("Output/tide_model.rda")

# Predict tide stage every minute for study period
dts <- seq(as.POSIXct("2018-01-19 17:00", tz = "UTC"),
           as.POSIXct("2018-06-01 11:00", tz = "UTC"),
           by = 60)
dts <- data.frame(date = as.Date(dts), ts = dts, tideHt = predict(tide_model, dts)) %>%
  mutate(tideHt_m = cut(tideHt, breaks = -6:6, right = FALSE))
dly_recv_log_tides <- filter(dly_recv_log, active) %>%
  left_join(dts, by = "date")
recv_tides <- dly_recv_log_tides %>%
  group_by(recvSiteName, tideHt_m) %>%
  summarize(hours = n()/60) %>%
  group_by(recvSiteName) %>%
  mutate(p_time = hours / sum(hours))

# Add tide heights to detections
rekn_chile_tides <- rekn_chile %>%
  mutate(tideHt = predict(tide_model, ts),
         tideHt_m = cut(tideHt, breaks = -6:6, right = FALSE)) %>%
  filter(spp == "REKN")

rekn_tides <- rekn_chile_tides %>%
  group_by(recvSiteName, recvDeployID, port, tideHt_m) %>%
  summarize(n_dets = n()) %>%
  group_by(recvSiteName) %>%
  mutate(p_time = n_dets / sum(n_dets)) %>%
  left_join(bahia_recvs, by = c("recvSiteName", "recvDeployID", "port"))

ggplot(rekn_tides, aes(x = tideHt_m, y = p_time)) + 
  geom_bar(data = recv_tides, aes(x = tideHt_m, y = p_time), 
           fill = "gray80", color = NA, stat = "identity") +
  geom_bar(aes(color = antBin), size = 1, fill = NA, stat = "identity") +
  facet_wrap(~ recvSiteName) + theme_bw() +
  scale_x_discrete(labels = every_nth(levels(rekn_tides$tideHt_m), 2, inverse = TRUE)) +
  labs(x = "Tide height (m) relative to Mean Sea Level (MSL)", y = "Proportion of time", 
       color = "Antenna\ndirection")
```


```{r, eval=FALSE}
# Send to dedicated page on personal website
rmarkdown::render("BL_REKN.Rmd", rmarkdown::html_document(pandoc_args = "--self-contained"), "~/R/adamdsmith.github.io/BL_REKN.html")
```

